Bayesian Exploration in Deep Reinforcement Learning

### 2022-07-22 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

Let \(\bm{Z}\) be a random variable defined over the support \(S \subseteq \R^n\)
and a continous probability density function \(q(\rvz)\). Further, let \(v\) be
a continous, differentiable and invertible function from \(S\) to
\(T \in \R^n\), if we let \(\bm{Z}^\prime = v(\bm{Z})\), then the probability
function \(q(\rvz^\prime)\) of \(\bm{Z}^\prime\) is given by
\begin{align}
  q(\rvz^\prime) &= q(\rvz) \left\lvert \det \left( \frac{\partial \rvz}{
    \partial \rvz^\prime} \right) \right\rvert \nonumber\\
  &= q(v^{-1}(\rvz^\prime)) \left\lvert \det \left( \frac{\partial}{\partial
  \rvz^\prime} v^{-1}(\rvz^\prime) \right) \right\rvert
  \label{eq:change_var_form1}\\
  &= q(v^{-1}(\rvz^\prime)) \left\lvert \det \left( \frac{\partial}{\partial
  \rvz^\prime} v(\rvz^\prime) \right) \right\rvert^{-1}
  \label{eq:change_var_form2}
\end{align}

@@

@@

We propose to use conditional normalizing flows to model the value distribution
\(Z^\pi\) with a continous estimate.

>>>>

Let \(\rvZ\) be a random variable defined over the support \(S \subseteq \R^n\)
and a continous probability density function \(q(\rvz)\). Further, let \(v\) be
a continous, differentiable and invertible function from \(S\) to
\(T \in \R^n\), if we let \(\rvZ^\prime = v(\rvZ)\), then the probability
function \(q(\rvz^\prime)\) of \(\rvZ^\prime\) is given by
\begin{align}
  q(\rvz^\prime) &= q(\rvz) \left\lvert \det \left( \frac{\partial \rvz}{
    \partial \rvz^\prime} \right) \right\rvert \nonumber\\
  &= q(v^{-1}(\rvz^\prime)) \left\lvert \det \left( \frac{\partial}{\partial
  \rvz^\prime} v^{-1}(\rvz^\prime) \right) \right\rvert
  \label{eq:change_var_form1}
  % &= q(v^{-1}(\rvz^\prime)) \left\lvert \det \left( \frac{\partial}{\partial
  % \rvz} v(\rvz) \right) \right\rvert^{-1}
  % \label{eq:change_var_form2}
\end{align}

@@

\subsection{Conditional Normalizing Flows} \label{sec:cnf}
Although normalizing flows is a good method for approximating distributions,
they do not directly facilitate learning conditional likelihoods.
\citet{winkler19} propose learning conditional distributions with
\emph{conditional normalizing flows}. Given a conditioning variable
\(\rvx \in U\), a random variale \(\rvZ \in S \subseteq \R^n\), and a continous,
differentiable function \(v : S \times U \rightarrow T\), bijective in \(S\) and
\(T\), the probability function \(q(\rvz^\prime)\), where
\(\rvz^\prime = v(\rvz, \rvx)\), can be expressed as

\begin{align}
  q(\rvz^\prime \vert \rvx) &= q(\rvz \vert \rvx) \left\lvert \det
  \left( \frac{\partial \rvz}{\partial \rvz^\prime} \right) \right\rvert
  \nonumber\\
  &= q(v^{-1}(\rvz^\prime, \rvx)) \left\lvert \det \left( \frac{\partial}
  {\partial \rvz^\prime} v^{-1}(\rvz^\prime, \rvx) \right) \right\rvert.
  \label{eq:cond_change_var_form1}
  % &= q(v^{-1}(\rvz^\prime; \rvx)) \left\lvert \det \left( \frac{\partial}
  % {\partial \rvz} v(\rvz; \rvx) \right) \right\rvert^{-1}
\end{align}

\noindent
Compared to Equation~\eqref{eq:change_var_form1}, all distributions are now
conditional, and the model has a conditional argument \(\rvx\).
\citet{winkler19} suggest three conditional modules:

\paragraph{Conditional Prior}
\begin{equation*}
  p(\rvz \vert \rvx) = \N(\rvz ; \mu(\rvx), \sigma^2(\rvx))
\end{equation*}
\paragraph{Conditional Split Prior}
\begin{equation*}
  p(\rvz_1 \vert \rvz_0, \rvx) =
  \N (\rvz ; \mu(\rvz_0, \rvx), \sigma^2(\rvz_0, \rvx))
\end{equation*}
\paragraph{Conditional Coupling}
\begin{equation*}
  \rvz^\prime_0 = 
  s(\rvz_1, \rvx) \cdot \rvz_0 + t(\rvz_1, \rvx); \qquad \rvz^\prime_1 = \rvz_1
\end{equation*}

The functions \(\mu\), \(\sigma^2\), \(s\) and \(t\) are implemented using
neural networks.

@@

We propose to use conditional normalizing flows to model the value distribution,
\(Z^\pi\), with a continous estimate. As opposed to quantile previous work on 
quantile regression methods, which aim to minimize the Wasserstein distance
to the target distribution, normalizing flows minimize KL-divergence. Our target
is thus the KL-divergence from the target to the value distribution
\footnote{Check order later}.

\begin{equation}
  \mathcal{L}_{\rvx,a}(\theta) \defeq \KL{\hat{\T}
  Z_{\tilde{\theta}}(\rvx,a)}{Z_{\theta}(\rvx,a)}
\end{equation}

Using conditional normalizing flows described in Section~\ref{sec:cnf}, we
define the value distribution model as an elementwise transformation of a
standard normal distribution conditioned on a low-dimensional representation of
the state \(\rvx\).

\begin{equation}
  Z_\theta(\rvx,a) = v_\theta^{-1}(z, \rvx^\prime)_a
\end{equation}
\begin{equation*}
  z \sim \N(0, I); \quad \rvx^\prime = h(\rvx)
\end{equation*}
